---
title: "TrendAnalysisSentimentAnalysisProject(Berja, Bibit, Buenvenida)"
author: "Bibit, Berja, Buenvenida"
date: "2024-12-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this research is to investigate popular sentiment toward BLACKPINK and its members throughout a period overlapping with both their Houston concert and the Itaewon tragedy. In particular in which, we want to:


1. Recognize how outside events affect mood and activity on social media of the people.

2. Give BLACKPINK's management team useful information on public opinion and involvements.

3. Determine important patterns and feelings to guide public relations management tactics during emergencie situations.

```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(tidytext)
library(sentimentr)
```
-- Data Loading and Inspection --
```{r}
# Load the dataset
data <- read.csv("/cloud/project/tweetsDF.csv")

# Inspect the structure of the data
str(data)

# Check for missing values
summary(data)

# Display the first few rows of the dataset
head(data)
```
-- Data Cleaning --

```{r}
# Data Cleaning
# Remove duplicates and handle missing values
data <- data %>% distinct() %>% drop_na()

# Ensure the dataset contains a 'created' column
if (!"created" %in% colnames(data)) {
  stop("The dataset does not contain a 'created' column. Please ensure the dataset includes a timestamp column for analysis.")
}

# Rename 'created' to 'datetime' for consistency
data <- data %>% rename(datetime = created)

# Convert 'datetime' to a proper date-time format
data <- data %>% mutate(datetime = ymd_hms(datetime))

# Text preprocessing: Remove URLs, hashtags, mentions, and special characters
data <- data %>% 
  mutate(text = str_remove_all(text, "http[s]?://\\S+|#\\w+|@\\w+|[^\\w\\s]"))

# Filter tweets mentioning Blackpink or its members
keywords <- c("Blackpink", "Rose", "Lisa", "Jennie", "Jisoo", "concert")
data_filtered <- data %>% filter(str_detect(tolower(text), paste(keywords, collapse = "|")))
```

-- Trend Analysis --

```{r}
# Restrict data to October 28–30, 2022
data_filtered <- data_filtered %>% 
  filter(datetime >= as.POSIXct("2022-10-28 00:00:00") & datetime <= as.POSIXct("2022-10-30 23:59:59"))

# Count tweets over time
time_trend <- data_filtered %>% 
  mutate(date = as.Date(datetime)) %>% 
  group_by(date) %>% 
  summarise(tweet_count = n())

# Ensure all dates in the range are included, even with zero counts
date_range <- seq(as.Date("2022-10-28"), as.Date("2022-10-30"), by = "day")
time_trend <- time_trend %>% 
  complete(date = date_range, fill = list(tweet_count = 0))

# Plot tweet trends over time
ggplot(time_trend, aes(x = date, y = tweet_count)) + 
  geom_line(color = "blue", size = 1) + 
  labs(title = "Tweet Trends for Blackpink and Members (Oct 28–30)", x = "Date", y = "Number of Tweets") + 
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 16), axis.title = element_text(size = 12))

```

Insights for Trend Analysis:

From October 28 to October 29, there was a steady increase in mentions of BLACKPINK and its members in tweets, but on October 30, there was a notable uptick in mentions. Discussions on the Itaewon incident and BLACKPINK's choice to go ahead with their Houston show correlate with the spike in activity on October 30. This analogy probably attracted more notice since people's opinions shifted from support to condemnation. By detecting important patterns and feelings, the surge also points to the magnifying impacts of social media, where high-profile events and debates frequently dominate discourse.

-- Sentiment Analysis --

```{r}
# Perform sentiment analysis on the filtered tweets
sentiment_scores <- sentiment_by(data_filtered$text)
data_filtered$sentiment <- sentiment_scores$ave_sentiment

# Categorize sentiment
data_filtered <- data_filtered %>% 
  mutate(sentiment_category = case_when(
    sentiment > 0 ~ "Positive",
    sentiment < 0 ~ "Negative",
    TRUE ~ "Neutral"
  ))

# Sentiment Distribution
ggplot(data_filtered, aes(x = sentiment_category, fill = sentiment_category)) + 
  geom_bar() + 
  labs(title = "Sentiment Distribution of BLACKPINK Tweets", x = "Sentiment", y = "Count") + 
  scale_fill_manual(values = c("Positive" = "green", "Neutral" = "gray", "Negative" = "red")) + 
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 16), axis.title = element_text(size = 12))


```
Insights for Sentiment Analysis:

Negative attitudes were the most common during this time, according to the sentiment analysis of tweets. Numerous tweets criticized BLACKPINK and their agency for going forward with their Houston show in spite of the Itaewon tragedy. A deeper look reveals that some of the unfavorable tweets seem to be the result of internet trolls escalating criticism. Though they are less common, positive comments show that fans are rooting for the group and praying for the people impacted by the Itaewon event. Since the majority of tweets on the tragedy and BLACKPINK's performance reflected strong thoughts or feelings, neutral sentiment was the least represented.