---
title: "TrendAnalysisSentimentAnalysisProject(Berja, Bibit, Buenvenida)"
author: "Bibit, Berja, Buenvenida"
date: "2024-12-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this research is to investigate popular sentiment toward BLACKPINK and its members throughout a period overlapping with both their Houston concert and the Itaewon tragedy. In particular in which, we want to:


1. Recognize how outside events affect mood and activity on social media of the people.

2. Give BLACKPINK's management team useful information on public opinion and involvements.

3. Determine important patterns and feelings to guide public relations management tactics during emergencie situations.

```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(tidytext)
library(sentimentr)
```
-- Data Loading and Inspection --
```{r}
# Load the dataset
data <- read.csv("/cloud/project/tweetsDF.csv")

# Inspect the structure of the data
str(data)

# Check for missing values
summary(data)

# Display the first few rows of the dataset
head(data)
```
-- Data Cleaning --

```{r}
# Data Cleaning
# Remove duplicates and handle missing values
data <- data %>% distinct() %>% drop_na()

# Ensure the dataset contains a 'created' column
if (!"created" %in% colnames(data)) {
  stop("The dataset does not contain a 'created' column. Please ensure the dataset includes a timestamp column for analysis.")
}

# Rename 'created' to 'datetime' for consistency
data <- data %>% rename(datetime = created)

# Convert 'datetime' to a proper date-time format
data <- data %>% mutate(datetime = ymd_hms(datetime))

# Text preprocessing: Remove URLs, hashtags, mentions, and special characters
data <- data %>% 
  mutate(text = str_remove_all(text, "http[s]?://\\S+|#\\w+|@\\w+|[^\\w\\s]"))

# Filter tweets mentioning Blackpink or its members
keywords <- c("Blackpink", "Rose", "Lisa", "Jennie", "Jisoo", "concert")
data_filtered <- data %>% filter(str_detect(tolower(text), paste(keywords, collapse = "|")))
```

-- Trend Analysis --

```{r}
# Restrict data to October 28–30, 2022
data_filtered <- data_filtered %>% 
  filter(datetime >= as.POSIXct("2022-10-28 00:00:00") & datetime <= as.POSIXct("2022-10-30 23:59:59"))

# Count tweets over time
time_trend <- data_filtered %>% 
  mutate(date = as.Date(datetime)) %>% 
  group_by(date) %>% 
  summarise(tweet_count = n())

# Ensure all dates in the range are included, even with zero counts
date_range <- seq(as.Date("2022-10-28"), as.Date("2022-10-30"), by = "day")
time_trend <- time_trend %>% 
  complete(date = date_range, fill = list(tweet_count = 0))

# Plot tweet trends over time
ggplot(time_trend, aes(x = date, y = tweet_count)) + 
  geom_line(color = "blue", size = 1) + 
  labs(title = "Tweet Trends for Blackpink and Members (Oct 28–30)", x = "Date", y = "Number of Tweets") + 
  theme_minimal() + 
  theme(plot.title = element_text(hjust = 0.5, size = 16), axis.title = element_text(size = 12))

```