---
title: "TrendAnalysisSentimentAnalysisProject(Berja, Bibit, Buenvenida)"
author: "Bibit, Berja, Buenvenida"
date: "2024-12-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this research is to investigate popular sentiment toward BLACKPINK and its members throughout a period overlapping with both their Houston concert and the Itaewon tragedy. In particular in which, we want to:


1. Recognize how outside events affect mood and activity on social media of the people.

2. Give BLACKPINK's management team useful information on public opinion and involvements.

3. Determine important patterns and feelings to guide public relations management tactics during emergencie situations.

```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(tidytext)
library(sentimentr)
```
-- Data Loading and Inspection --
```{r}
# Load the dataset
data <- read.csv("/cloud/project/tweetsDF.csv")

# Inspect the structure of the data
str(data)

# Check for missing values
summary(data)

# Display the first few rows of the dataset
head(data)
```
